The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-11-23 outputs/docs/events/slides/slides.Rmd
Update paper

---
title: The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)
subtitle: 
author:
- Monica Alexander, University of Toronto\newline
- Rohan Alexander, Australian National University
date: 25 October 2018
institute: Presentation at the Research School of Economics, Australian National University, Canberra, Australia.
output: binb::metropolis
# output: ioslides_presentation
fontsize: 12pt
---

@@

elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
top_words <- read_csv2(here::here("outputs/misc/top_words_40.csv"), col_types = cols())
missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())

elections_results <- read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>% 
  # filter(Significant %in% c("Yes", "No"))
  filter(Significant %in% c("Yes"))

governments_results <- read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>% 
  filter(Significant %in% c("Yes")) %>% 
  # filter(Significant %in% c("Yes", "No")) %>% 
  select(-Party, -`Died in Office`)

key_events_results <- read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols())
#breka
```

@@

- Changes in government tend be associated with topic changes even when the party in power does not change.
- Elections that do not result in a change in government are rarely associated with topic changes.
- Economic events, such as financial crises, have less significant effects than other events such as terrorist attacks.
- The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.

@@

## Hansard
- A daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901. It's not vertatim, but it's pretty close.
- Hansard records have been used in other counties but not really at scale in Australia (although others, such as Patrick Leslie, also use them).
- Daily PDFs are available Hansard records available online as PDFs and these are considered the official release. 
- There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.

@@

## Correlated Topic Model
Modification of LDA - rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in step 2 in LDA above, CTM assumes
$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
Essentially it swaps the Dirichlet for the Logistic Multivariate Normal. This sounds easy, but it's hard to implement.

@@

```{r exampletopics, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../../../figures/topics_example-slides.png")
```

## Structural Topic Model
The Structural Topic Model approach then adds a covariate to $\mu$ which allows consideration of additional information. 
$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
Again, sounds easy, but hard to implement, and they have a very nice solutions algorithm.

@@

We choose 40 topics because it is the minimum needed to have meaningful results.

@@

elections_results %>%
  select(-Significant) %>% 
  kable() %>%
  kable_styling(font_size = 10)

@@

governments_results %>%
  select(-Significant) %>% 
  kable() %>%
  kable_styling(font_size = 10)

@@

key_events_results %>%
  kable() %>%
  kable_styling(font_size = 10)
#CAS
```

@@

>>>>

---
title: The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)
subtitle: 
author:
- Monica Alexander, University of Toronto\newline
- \textbf{Rohan Alexander, Australian National University}
date: 22 November 2018
institute: Presentation at the University of Toronto Political Behaviour Group, Toronto, Canada.
output: binb::metropolis
# output: ioslides_presentation
fontsize: 12pt
---

@@

elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
top_words <- read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols())
missing_days <- read_csv(here::here("outputs/misc/missing_dates.csv"), col_types = cols())
hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())

elections_results <-
  read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>%
    filter(Significant %in% c("Yes")) %>%
    select(-Significant)

governments_results <-
  read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>%
    filter(Significant %in% c("Yes")) %>%
    select(-Party,-`Died in Office`,-Significant)

key_events_results <- read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols())
#breka

key_events_results_cols <-
  read_csv(here::here("outputs/results-analysis_model/results-outliers_in_columns.csv"), col_types = cols())

names(key_events_results_cols) <- c("Dates", "", "", "", "", "", "", "")

key_events_results_cols <- key_events_results_cols[7:8]

names(key_events_results_cols) <- c("Dates", "")

@@

- Changes in government tend be associated with topic changes even when the party in power does not change.
- Elections that do not result in a change in government are rarely associated with topic changes.
- The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.

@@

## Hansard
- A daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901. It's not vertatim, but it's pretty close.
- Hansard records have been used in other counties but not really at scale in Australia.
- Daily PDFs are available online and these are considered the official release. 
- There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.

@@

## Correlated Topic Model
Modification of LDA - rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in LDA, CTM assumes
$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
Essentially it swaps the Dirichlet for the Logistic Multivariate Normal. This sounds easy, but it's hard to implement.

@@

```{r exampletopics, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../../../figures/topics_example_slides_update.png")
```

## Structural Topic Model
The Structural Topic Model approach then adds a covariate to $\mu$ which allows consideration of additional information. 
$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
Again, sounds easy, but hard to implement, and they have a very nice algorithm.

@@

We choose 80 topics because it is the minimum needed to have meaningful results.

@@

elections_results %>%
  filter(Number %in% c(9, 10, 19, 21, 22, 23, 28, 30, 32, 33)) %>% 
  kable() %>%
  kable_styling(font_size = 10)

## Analysis model - Significantly different elections (cont.)

```{r electionsresultscont, echo = FALSE, results = 'asis'}

elections_results %>%
  filter(Number %in% c(34, 35, 36, 38, 39, 40, 41, 42, 43, 44)) %>% 
  kable() %>%
  kable_styling(font_size = 10)

@@

governments_results %>%
  filter(Number %in% c(6, 9, 10, 12, 14, 15, 16, 20, 21, 22)) %>% 
  kable() %>%
  kable_styling(font_size = 10)

## Analysis model - Significantly different governments (cont.)

```{r governmentsresultscont, echo = FALSE, results = 'asis'}

governments_results %>%
  filter(Number %in% c(24, 25, 26, 27, 28, 29, 30, 31, 32, 34)) %>% 
  kable() %>%
  kable_styling(font_size = 10)

@@

key_events_results_cols %>%
  kable() %>%
  kable_styling(font_size = 10)

@@

# Supplementary
